What We Eval in the Shadows

### 2021-04-09 paper/main.tex
tax

\begin{itemize}
\item \underline{$min(e)=\c{V}$}: Expression that represent values are
  frequently passed to \eval. The majority of those, \packageValOneNodePercent,
  are inline constants (integers or doubles). The rest trivially evaluate to a
  value.\footnote{True as long as base functions such as \c{+} are not
  redefined. They typically aren't, but this is a limitation of this
  categorization.} In our corpus, \packageNbCallSitesUniqueActualValue call
  sites only ever see a simple values; the median number of times they are
  exercised is \packageMedianRunSitesUniqueActualValue, suggesting a possible
  lack of coverage. However, manual inspection reveals cases such as:
\begin{lstlisting}
 f1 <- eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
  This concatenates to a string and \eval simply returns it as is.
  From twenty randomly selected \evals, only \packageUsefulValueEvalPercent of
  them needed to use \eval.
\item \underline{$min(e)=\c{X}$}: Variables are the most common form. They
  subsume values, thus \c{X} includes arithmetic expressions in which a variable
  occurs. \packageNbSymbolVarSitePercent of variable expression are symbols, \ie
  just an \c{x}. As a variable may refer to a promise, it may trigger
  computation.
\item \underline{$min(e)=\c{\$}$}: A name lookup, \c{x\$f}, can be used to
  access variable in an environment or a column in a data frame, this also
  include vector   indexing operators, \c{[]} and \c{[[]]}. A name lookup
  subsumes variables.
\item \underline{$min(e)=$~\c{<-}}: Assignments account for
  \packageAssignSitesPercent of \eval sites, they are \c{<-}, {\tt <<-} and
  \c{assign}, and they subsume named lookups.
\item \underline{$min(e)=\c{F()}$}: A plain function call which may have some
  values as argument but does not include variables. It should be noted that
  function name require variable lookups -- we distinguish those as they usually
  do not trigger computation.
\item \underline{$min(e)=\c{F(X)}$}: Function calls whose arguments may include
  variable references.
\item \underline{$min(e)=\c{F(F(X))}$}: Nested function calls with variables.
\item \underline{$min(e)=\c{FUN}$}: Function definition accounts for
  \packageFunctionDefinitionSitesPercent of \eval sites. In addition the
  functions inside other expressions account for
  \packageGeneralizedFunctionDefinitionSitesPercent of sites, and give an
  estimate of the use of higher-order functions.
\item \underline{$min(e)=\c{\{\,\}}$}: Arbitrary-length statement blocks. These
  are larger expressions with, on average, \packageMinimizedoperationsjRnd
  instructions. The contents of the block are not inspected.
\item \underline{$min(e)=\c{model.frame}$}: Call to the \c{model.frame} function
  used to create statistical models. This subsume all other categories.

\end{itemize}

>>>>

\newcommand{\EE}[1]{{{\emph{\framebox{#1}}}}}

\medskip\noindent\EE{$min(e)=\c{V}$} Expression that represent values are
frequently passed to \eval. The majority of those, \packageValOneNodePercent,
are inline constants (integers or doubles). The rest trivially evaluate to a
value.\footnote{True as long as base functions such as \c{+} are not redefined.
They typically aren't, but this is a limitation of this categorization.} In our
corpus, \packageNbCallSitesUniqueActualValue call sites only ever see a simple
values; the median number of times they are exercised is
\packageMedianRunSitesUniqueActualValue, suggesting a possible lack of coverage.
However, manual inspection reveals cases such as:
\begin{lstlisting}
 f1 <- eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
  This concatenates to a string and \eval simply returns it as is.
  From twenty randomly selected \evals, only \packageUsefulValueEvalPercent of
  them needed to use \eval.

\medskip\noindent\EE{$min(e)=\c{X}$} Variables are the most common form. They
subsume values, thus \c{X} includes arithmetic expressions in which a variable
occurs. \packageNbSymbolVarSitePercent of variable expression are symbols, \ie
just an \c{x}. As a variable may refer to a promise, it may trigger computation.

\medskip\noindent\EE{$min(e)=\c{\$}$} A name lookup, \c{x\$f}, can be used to
access variable in an environment or a column in a data frame, this also include
vector indexing operators, \c{[]} and \c{[[]]}. A name lookup subsumes
variables.

\medskip\noindent\EE{$min(e)=$~\c{<-}} Assignments account for
\packageAssignSitesPercent of \eval sites, they are \c{<-}, {\tt <<-} and
\c{assign}, and they subsume named lookups.

\medskip\noindent\EE{$min(e)=\c{F()}$} A plain function call which may have some
values as argument but does not include variables. It should be noted that
function name require variable lookups -- we distinguish those as they usually
do not trigger computation.

\medskip\noindent\EE{$min(e)=\c{F(X)}$} Function calls whose arguments may include
variable references.

\medskip\noindent\EE{$min(e)=\c{F(F(X))}$} Nested function calls with variables.

\medskip\noindent\EE{$min(e)=\c{FUN}$} Function definition accounts for
  \packageFunctionDefinitionSitesPercent of \eval sites. In addition the
  functions inside other expressions account for
  \packageGeneralizedFunctionDefinitionSitesPercent of sites, and give an
  estimate of the use of higher-order functions.

\medskip\noindent\EE{$min(e)=\c{\{\,\}}$} Arbitrary-length statement blocks.
These are larger expressions with, on average, \packageMinimizedoperationsjRnd
instructions. The contents of the block are not inspected.

\medskip\noindent\EE{$min(e)=\c{model.frame}$} Call to the \c{model.frame}
function used to create statistical models. This subsume all other categories.
